\documentclass[12pt]{book}
\usepackage[intlimits,sumlimits,namelimits]{amsmath}
\usepackage{amssymb}
\usepackage[mathscr]{eucal}
\usepackage{mathrsfs}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amsmath}
%\usepackage{times}

\usepackage[dvips]{graphicx}
\usepackage{epsf}
\usepackage{epsfig}
\usepackage{fancyhdr}
\usepackage{layout}

\usepackage[french]{babel}
\usepackage[T1]{fontenc}
\usepackage[latin1]{inputenc}

\input{Macro.tex}
\input{commandes.tex}

%% ENTETE DE FRANCOIS
%\documentclass[12pt,a4paper,twoside,final,notitlepage]{book}
%\usepackage[dvips]{graphicx}
%\usepackage[leqno]{amsmath}
%\usepackage{a4}
%\usepackage{epsf}
%\usepackage{epsfig}
%\usepackage{amsfonts}
%\usepackage{amssymb}
%\usepackage{french}
%\usepackage[T1]{fontenc}
%\pagestyle{myheadings}
%% FIN ENTETE DE FRANCOIS


%\pagestyle{fancy}
%\pagestyle{empty}
%\pagestyle{myheadings}
%\setcounter{part}{arabic}
%\numberwithin{section}{chapter}
%\numberwithin{equation}{chapter}
%\numberwithin{theorem}{chapter}
\begin{document} 
\begin{titlepage}
\title{
\vspace{1cm}
\begin{large}
Analyse Mathématique et Numérique du Rayonnement Acoustique des Turbor\'eacteurs \\
\end{large}
}
\author{Stefan Duprey\thanks{EADS-CCR Suresnes, D\'epartement Mod\'elisation Math\'ematique et Num\'erique; Institut Elie Cartan-INRIA Lorraine-Universit\'e Poincar\'e Nancy 1}
\\
}
\date{} 
\maketitle
\end{titlepage}
\pagestyle{empty}
\input{remerciements}
\newpage
\pagestyle{myheadings}
\tableofcontents
\newpage
\input{Introductionthesis}
\input{problemepose}
\input{modesaumoteur}
\input{ecoulementconstant}
\input{ondesavecheterogeneite}
\input{ecoulementpotentiel}
\input{numeriqueglobal}
\newpage
\input{Conclusionthesis}
\begin{thebibliography}{1}
\bibitem{TA}
T.~Abboud,
\newblock{\em Etude math\'ematique et num\'erique de quelques probl\`emes de diffraction d'ondes \'electromagn\'etiques.}
\newblock Th\`ese de doctorat de l'\'ecole polytechnique, (1991), France.
\bibitem{TAJCN}
T.~Abboud et J.C.~N\'ed\'elec,
\newblock{\em Electromagnetic waves in inhomogenous medium.}
\newblock J. Math. Anal. Appl., 164 (1992), pp. 40-58.
\bibitem{RJAWE}
R.J.~Astley et W.~Eversman,
\newblock{\em A finite element formulation of the eigenvalue problem in lined ducts with flow.}
\newblock J. Sound Vibration, 65 (1979), pp. 61-74.
\bibitem{BA}
B.~Aublin,
\newblock{\em Rayonnement et diffraction acoustique par un guide ouvert semi-infini.}
\newblock Th\`ese de doctorat de l'universit\'e de Compi\`egne, France, 1996.
\bibitem{CBDJ}
C.~Bailly et D.~Juv\'e,
\newblock{\em Numerical solution of acoustic propagation problems using linearized Euler equations.}
\newblock AIAA J., 36 (1998), pp. 775-782.
\bibitem{EBSFPJ}
E.~B\'ecache, S.~Fauqueux et P.~Joly,
\newblock{\em Stability of perfectly matched layers, group velocities and anisotropic waves.}
\newblock J. Comp. Phys., 188 (2003), pp. 399-433.
\bibitem{JPB}
J.-P.~B\'erenger,
\newblock{\em A perfectly matched layer for the absorption of electromagnetic waves.}
\newblock J. Comput. Phys., 114 (1994), pp. 185-200.
\bibitem{HBGWWW}
H.~Berger, G.~Warnecke et W.L.~Wendland,
\newblock{\em Coupling of FEM and BEM for transsonic flows.}
\newblock The Mathematics of finite elements and applications, 95 (1994), pp. 323-350.
\bibitem{MBSP}
M.~Bernacki et S.~Piperno,
\newblock{\em M\'ethode de type Galerkin discontinu appliqu\'ee aux \'equations d'Euler lin\'earis\'ees en \'ecoulement uniforme ou non.}
\newblock INRIA, RR-5292, 2004.
\bibitem{BDM}
C.~Bernardi, M.~Dauge et Y.~Maday,
\newblock {\em Spectral Methods for Axisymmetric Domains.}
\newblock Series  "Series in Applied Mathematics", 3, Elsevier, 1999
\bibitem{CBCBDJ}
C.~Bogey, C.~Bailly et D.~Juv\'e,
\newblock{\em Computation of flow noise using source terms in linearized Euler's equations.}
\newblock AIAA J., 40 (2002), pp. 235-243.
\bibitem{ASBBDLDELVP}
A.-S.~Bonnet-Ben Dhia, L.~Dahi, E.~Lun\'eville et V.~Pagneux,
\newblock{\em Acoustic Diffraction by a plate in a uniform flow.}
\newblock Math. Models Methods Appl. Sci., 12 (2002), pp. 625-647.
\bibitem{ADLB}
A. De La~Bourdonnaye,
\newblock{\em Some formulations coupling finite element and integral equation methods for Helmholtz equation and electromagnetism.}
\newblock Numer. Math., 69 (1995), pp. 257-268. 
\bibitem{MOBRGJPPPOPGP}
M.O.~Bristeau, R.~Glowinski, J.~Periaux, P.~Perrier, O.~Pironneau et G.~Poirier,
\newblock{\em On the numerical solution of nonlinear problems in fluid dynamics by least squares and finite element methods.}
\newblock{Comput. Methods Appl. Mech. Engrg, 51 (1985), pp. 363-394.}
\bibitem{HB}
H.~Br\'ezis,
\newblock{\em Analyse fonctionnelle.}
\newblock Masson, Paris, France, 1998.
\bibitem{MB}
M.~Bruneau,
\newblock{\em Manuel d'acoustique fondamentale.}
\newblock Herm\`es, Paris, France, 1998.
\bibitem{PGC}
P.G.~Ciarlet,
\newblock{\em The Finite Element Method for Elliptic Problems.}
\newblock Series  "Studies in Mathematics and its Applications", North-Holland, Amsterdam, 1978. 
\bibitem{JFCMPGT}
J.F.~Ciavaldini, M.~Pogu et G.~Tournemine,
\newblock{\em Existence aud regularity of stream functions for subsonic flows past profiles with a sharp trailing edge.}
\newblock{Arch. Rat. Mech. Anal., 93 (1986), pp. 1-14.}
\bibitem{MC}
M.~Costabel,
\newblock{\em Boundary integral operators on Lipschitz domains : Elementary results.}
\newblock SIAM J. Math. Anal., 19 (1988), pp. 613-626.
\bibitem{MCMD}
M.~Costabel et M.~Dauge,
\newblock{\em Weighted regularization of Maxwell equations in polyhedral domains.}
\newblock Numer. Math., 93 (2002), pp. 239-277.
\bibitem{JPC}
J.P.~Coyette,
\newblock{\em Manuel th\'eorique ACTRAN.}
\newblock Free Field Technologies, Louvain-la-Neuve, Belgique, 2001.
\bibitem{JPCBVDN}
J.P.~Coyette et B. Van den~Nieuwenhof,
\newblock{\em A conjugate infinite element method for half-space acoustic problems.}
\newblock The J. of Acoustical American Society, 108 (2000), pp. 1464-1473.
\bibitem{JPCBVDNBVDN}
J.P.~Coyette et B. Van den~Nieuwenhof,
\newblock{\em Treatment of frequency-dependent admittance boundary conditions in transient acoustic finite/infinite element models.}
\newblock The J. of Acoustical American Society, 110 (2001), pp. 1743-1751.
\bibitem{DGC}
D.G.~Crighton,
\newblock{\em Basic principles of aerodynamic noise generation.}
\newblock Progress in Aerospace Sciences, 16 (1975), pp. 31-96.
\bibitem{NC}
N.~Curle,
\newblock{\em The influence of solid boundaries upon aerodynamic sound.}
\newblock Proceedings of the royal society of London, 231 (1955), pp. 505-514.
\bibitem{IDRWE}
I.~Danda Roy et W.~Eversman,
\newblock{\em Improved finite element modeling of the turbofan engine inlet radiation problem.}
\newblock J. Vib. Acoust., 117 (1995), pp. 109-115.
\bibitem{LD}
L.~Dahi,
\newblock{\em Guidage et diffraction d'ondes acoustiques : \'etude math\'ematique et analyse num\'erique.}
\newblock Th\`ese de doctorat de l'universit\'e Paris 6, Paris, 2001.
\bibitem{ADIT}
A.~Delnevo et I.~Terrasse,
\newblock{\em Manuel th\'eorique ACTI3S, Justifications Th\'eoriques.}
\newblock Technical report, Rapport interne Aerospatiale Matra-CCR, 2000. 
\bibitem{WEDO}
W.~Eversman et D.~Okunbor,
\newblock{\em Aft fan duct acoustic radiation.}
\newblock J. of Sound and Vibrations. 1997.
\bibitem{REWS}
R.~Ewert et W.~Schröder, 
\newblock{\em Acoustic perturbation equations based on flow decomposition via source filtering.}
\newblock J. Computat. Physics, 188 (2003), pp. 365-398.
\bibitem{MR}
B.~Mercier et G.~Raugel,
\newblock{\em R\'esolution d'un probl\`eme aux limites dans un ouvert axisym\'etrique par \'el\'ements finis en (r,z) et s\'erie de Fourier en $\theta$.}
\newblock R.A.I.R.O Analyse num\'erique, 16 (1982), pp. 405-461.
\bibitem{VGPAR}
V.~Girault et P.-A.~Raviart, 
\newblock{\em Finite element methods for Navier-Stokes equations, theory and algorithms.}
\newblock vol. 5 of Springer Series in computational mathematics, Springer-Verlag, Berlin, Germany, 1986.
\bibitem{NG}
N.~Gmati,
\newblock{\em Guidage et diffraction d'ondes en milieu non born\'e.}
\newblock Ph.D. thesis, Universit\'e Pierre et Marie Curie, Paris, 1992.
\bibitem{PG}
P.~Grisvard,
\newblock{\em Elliptic problems in nonsmooth domains.}
\newblock vol. 24 of Monographs and studies in mathematics, Pitman, London, 1985.
\bibitem{MSH}
M.S.~Howe,
\newblock{\em Theory of vortex sound.}
\newblock Cambridge texts in applied mathematics, Cambridge university press, 2003.
\bibitem{TK}
T.~Kato,
\newblock{\em Perturbation theory for linear operators.}
\newblock Springer-Verlag, New-York, NY, USA, 1976. 
\bibitem{LK}
Lord~Kelvin,
\newblock{\em On vortex motion.}
\newblock Transactions of the royal society of Edinburgh. 25 (1867), pp. 217-260.
\bibitem{GL}
G.~Legendre,
\newblock{\em Rayonnement acoustique dans un fluide en \'ecoulement : analyse math\'ematique et num\'erique de l'\'equation de Galbrun.}
\newblock Th\`ese de doctorat, Universit\'e Pierre et Marie Curie, Paris, France, 2003.
\bibitem{VL}
V.~Levillain,
\newblock{\em Couplage \'el\'ements finis-\'equations int\'egrales pour la r\'esolution des \'equations de Maxwell en milieu h\'et\'erog\`ene.}
\newblock Th\`ese de l'\'ecole polytechnique, France, 1991.
\bibitem{SLHBSTADMR}
S.~Lidoine, H.~Batard, S.~Troyes, A.~Delnevo et M.~Roger,
\newblock{\em Acoustic radiation modelling of aeroengine intake, comparaison between analytical and numerical methods.}
\newblock $7^{th}$ AIAA/CEAS Aeroacoustics conference, paper 2001-2140.
\bibitem{MJL}
M.J.~Lighthill,
\newblock{\em On sound generated aerodynamically. Part one : general theory.}
\newblock Proceedings of the royal society of London, 211 (1952), pp. 564-587.
\bibitem{JLLEM}
J.L.~Lions et E.~Magenes,
\newblock{\em Probl\`emes aux limites non homog\`enes et applications.}
\newblock Dunod, 1968, Paris.
\bibitem{FMFD}
F.~Mar\'echal et F.~Dubois,
\newblock{\em Manuel th\'eorique A3DF. Diff\'erences finies pour la propagation acoustique en pr\'esence d'un \'ecoulement stationnaire uniforme.}
\newblock Technical report, EADS-CCR, Juillet 2000.
\bibitem{HJPMRO}
H. J.-P.~Morand et R.~Ohayon,
\newblock{\em Interactions fluides-structures.}
\newblock Recherches en math\'ematiques appliqu\'ees , vol. 23, Masson, Paris, France, 1992.
\bibitem{MKM}
M.K.~Myers,
\newblock{\em On the acoustic boundary condition in the presence of flow.}
\newblock J. Sound Vibration, 71 (1980), pp. 429-434.
\bibitem{FM}
F.~Murat,
\newblock{\em L'injection du c\^one positif de $H^{-1}$ dans $W^{-1,q}$ est compact pour tout $q<2$.}
\newblock J. Math. Pures Appl., 60 (1981), pp. 309-322.
\bibitem{JCN}
J.-C.~N\'ed\'elec,
\newblock{\em Ondes electromagn\'etiques et acoustiques.}
\newblock Cours de D.E.A, Universit\'e Paris 6, 1993.
\bibitem{JCNJCN}
J.-C.~N\'ed\'elec,
\newblock{\em Mixed finite elements in $\mathbb{R}^3$.}
\newblock Numer. Math., 35 (1980), pp. 315-341.
\bibitem{JN}
J.~Ne$\check{c}$as,
\newblock{\em Compacit\'e par entropie et ecoulements de fluides.}
\newblock Notes de cours de Universit\'e Charles Pragues-E.N.S Paris, Masson, Paris, 1989. 
\bibitem{VP}
V.~Pagneux,
\newblock{\em Propagation acoustique dans les guides \`a section variables et effets d'\'ecoulement.}
\newblock Th\`ese de doctorat, Universit\'e du Maine, France, 1996.
\bibitem{AVPWE}
A.V.~Parrett et W.~Eversman,
\newblock{\em Wave envelope and finite element approximation for turbofan noise radiation in flight.}
\newblock AIAA J., 24 (1986), pp. 753-760. 
\bibitem{JP}
J.~Perriaux,
\newblock{\em Three dimensional analysis of compressible potential flows with the FEM.}
\newblock Method. Int. Jour. for Num. Math. in Engrg., 9 (1975).
\bibitem{CPGE}
C.~Peyret et G.~Elias,
\newblock{\em Finite-element method to study harmonic aeroacoustics problems.}
\newblock J. Acoust. Soc. Amer., 110 (2001), pp. 661-668.
\bibitem{BP}
B.~Poir\'ee,
\newblock{\em Les \'equations de l'acoustique lin\'eaire et non lin\'eaire dans un \'ecoulement de fluide parfait.}
\newblock Acustica, 57 (1985), pp. 5-25.
\bibitem{PARJMT}
P.-A.~Raviart et J.-M.~Thomas,
\newblock{\em A mixed finite element method for second order elliptic problems.}
\newblock Springer-Verlag, Berlin, Germany, 1977.
\bibitem{FR}
F.~Rellich,
\newblock{\em Über das asymptotische Verhalten der lösungen von $\Delta u+\lambda u=0$ in unendlichen Gebieten.}
\newblock Jahresber. Deutsch. Math. Verein., 53 (1943), pp. 57-65.
\bibitem{GS}
G.~Sylvand,
\newblock{\em La méthode multipôle rapide en électromagnétisme : Performances, parallélisation, applications.}
\newblock Thèse de doctorat, Université de Nice-Sophia Antipolis, Juin 2002.
\bibitem{CKWT}
C.K.W.~Tam,
\newblock{\em Computational aeroacoustics : issues and methods.}
\newblock AIAA J.,  33 (1995), pp. 1788-1796.
\bibitem{CKWTCKWT}
C.K.W.~Tam,
\newblock{\em Advances in numerical boundary conditions for computational aeroacoustics.}
\newblock J. Comput. Phys., 144 (1998), pp. 213-234.
\bibitem{CKWTJCW}
C.K.W.~Tam et J.C.~Webb,
\newblock{\em Dispersion-relation-preserving finite difference schemes for computational acoustics.}
\newblock J. Comput. Phys., 107 (1993), pp. 262-281.
\bibitem{ITAT}
I.~Terrasse et A.~Tillequin,
\newblock {\em ELFI2R 3.1. Rapport sur la prise en compte des mat\'eriaux anisotropes.}
\newblock Technical report, EADS-CCR, Janvier 2003.
\bibitem{AT}
A.~Tillequin,
\newblock{\em Une m\'ethode de raccordement modal g\'en\'eralis\'ee pour les probl\`emes de jonction de guides d'ondes.}
\newblock Rapport de recherche 345, ENSTA, Paris, France, 2001.
\bibitem{JEFWDLH}
J.E.~Ffowcs Williams et D.L. Hawkings,
\newblock{\em Sound generation by turbulence and surfaces in arbitrary motion.}
\newblock Philosophical transactions of the royal society of London, 264 (1969), pp. 321-342.
\bibitem{KSY}
K.S.~Yee,
\newblock{\em Numerical Solution of Initial Boundary Value Problems in Isotropic Media.}
\newblock IEEE Trans. Antennas Propagation, 1966.
\end{thebibliography}
%\newpage
%\appendix
%\input{OperateursSurfaciques}
%\input{Sobolev}
%\input{ElementsFinisRappel}
%\include{RoutineVol}
\end{document}
